INTELLIGENT SYSTEMS

### 2021-04-10 paper_6.tex
start 6.4

>>>>

\subsubsection{Model Parameterization}
In summary, to generate high-quality semantic segmentation masks, it is 
required to take an image from the ImgNet dataset and submit it to the 
following steps:
\begin{enumerate}
    \item Create a first mask ($ mask_c $) with a non-superivisoned network \cite{0876055520};
    \item Improve maskc with the GrabCut model \cite{0876055542} to generate a new mask ($ mask_e $);
    \item Train DeepLab network \cite{0876055502} with $ mask_e $;
    \item Generate a better mask ($ mask_r $) using the original ImgNet image;
    \item Enhance the generated mask ($ mask_e $) by applying the GrubCut method;
    \item Repeat from step 3 until the best mask will be obtained.
\end{enumerate}

\subsubsection{Extended the Proposed Framework to Foreground Segmentation}
In order to use the proposed framework in a foreground object recognition 
problem, only the part concerning the enhanced of the mask must be replaced 
with a code that allows to perform the required task. With an architecture 
similar to \emph{FPN} \cite{0876055543}, the new network is called the \emph{Dilated Feature Pyramid 
Network} (DFPN). This network has several dilated layers, in three branches, 
added to enlarge the receptive field of the network (Fig \ref{fig:DFPN}). The features generated 
by these layers are aggregated to make a prediction.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8 \linewidth]{images/paper6/DFPN.png}
    \centering
    \caption{DFPN architecture.}
    \label{fig:DFPN}
\end{figure}

\subsection{EXPERIMENTS}
